\sys: Light-touch Data-Parallel Shell Processing

### 2020-05-05 pldi/draft.tex
Update structure

%% Title information
%% \title{Dish: Distribution-oblivious Shell Scripting}         %% [Short Title] is optional;
\title{\sys: Automated Data-Parallel Shell Processing}         %% [Short Title] is optional;
%% \title{Extensible data processing in the shell}

@@

%% Author with single affiliation.
\author{First1 Last1}
%% \authornote{with author1 note}          %% \authornote is optional;
%%                                         %% can be repeated if necessary
%% \orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
%% \affiliation{
%%   \position{Position1}
%%   \department{Department1}              %% \department is recommended
%%   \institution{Institution1}            %% \institution is required
%%   \streetaddress{Street1 Address1}
%%   \city{City1}
%%   \state{State1}
%%   \postcode{Post-Code1}
%%   \country{Country1}                    %% \country is recommended
%% }
%% \email{first1.last1@inst1.edu}          %% \email is recommended

%% Author with two affiliations and emails.
\author{First2 Last2}
%% \authornote{with author2 note}          %% \authornote is optional;
%%                                         %% can be repeated if necessary
%% \orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
%% \affiliation{
%%   \position{Position2a}
%%   \department{Department2a}             %% \department is recommended
%%   \institution{Institution2a}           %% \institution is required
%%   \streetaddress{Street2a Address2a}
%%   \city{City2a}
%%   \state{State2a}
%%   \postcode{Post-Code2a}
%%   \country{Country2a}                   %% \country is recommended
%% }
%% \email{first2.last2@inst2a.com}         %% \email is recommended
%% \affiliation{
%%   \position{Position2b}
%%   \department{Department2b}             %% \department is recommended
%%   \institution{Institution2b}           %% \institution is required
%%   \streetaddress{Street3b Address2b}
%%   \city{City2b}
%%   \state{State2b}
%%   \postcode{Post-Code2b}
%%   \country{Country2b}                   %% \country is recommended
%% }
%% \email{first2.last2@inst2b.org}         %% \email is recommended

@@

\TODO{Drop the automated from the title maybe?}

@@

@@

\heading{Take-away}
\sys leads to significant performance improvements in completely unmodified \unix pipelines found out in the wild.
Small tweaks can yield further improvements, showing that \sys-awareness and scripting expertise can improve results.

@@

\heading{Take-away}
Multi-line Java Program parallel program decomposed in two phases---a highly parallel map phase and a sequential reduce phase---corresponds to a much smaller shell script with

@@

\heading{Take-away}

@@

\heading{Take-away}
\sys does not improve performance when running the risk of breaking correctness. % This should go in the intro
% Compared to \sys, \ttt{parallel} can lead to a combination of smaller performance improvements, incorrect execution with respect to the sequential program, and higher rewriting effort.
In highly-parallel benchmarks, \sys can lead to performance that is comparable to highly specialized streaming frameworks---at a fraction of the cost in terms of manual development.

>>>>

%% Title information
%% \title{Dish: Distribution-oblivious Shell Scripting}         %% [Short Title] is optional;
\title{\sys: Light-touch Data-Parallel Shell Processing}         %% [Short Title] is optional;
%% \title{Extensible data processing in the shell}

@@

%% Author with single affiliation.
\author{
  Anonymous Author(s)
  \normalsize{Additional Anonymized Material: \href{https://github.com/u-3/dish}{https://github.com/u-3/dish}.}
}
%% \authornote{with author1 note}          %% \authornote is optional;
%%                                         %% can be repeated if necessary
%% \orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
%% \affiliation{
%%   \position{Position1}
%%   \department{Department1}              %% \department is recommended
%%   \institution{Institution1}            %% \institution is required
%%   \streetaddress{Street1 Address1}
%%   \city{City1}
%%   \state{State1}
%%   \postcode{Post-Code1}
%%   \country{Country1}                    %% \country is recommended
%% }
%% \email{first1.last1@inst1.edu}          %% \email is recommended

%% Author with two affiliations and emails.
% \author{First2 Last2}
%% \authornote{with author2 note}          %% \authornote is optional;
%%                                         %% can be repeated if necessary
%% \orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
%% \affiliation{
%%   \position{Position2a}
%%   \department{Department2a}             %% \department is recommended
%%   \institution{Institution2a}           %% \institution is required
%%   \streetaddress{Street2a Address2a}
%%   \city{City2a}
%%   \state{State2a}
%%   \postcode{Post-Code2a}
%%   \country{Country2a}                   %% \country is recommended
%% }
%% \email{first2.last2@inst2a.com}         %% \email is recommended
%% \affiliation{
%%   \position{Position2b}
%%   \department{Department2b}             %% \department is recommended
%%   \institution{Institution2b}           %% \institution is required
%%   \streetaddress{Street3b Address2b}
%%   \city{City2b}
%%   \state{State2b}
%%   \postcode{Post-Code2b}
%%   \country{Country2b}                   %% \country is recommended
%% }
%% \email{first2.last2@inst2b.org}         %% \email is recommended

@@

% \TODO{Drop the automated from the title maybe?}
% \nv{Updates}

@@

We attribute the small drop above $96\times$ in \ttt{spell} \ttt{sort} \ttt{wf}
and \ttt{bi-grams} to a combination of hyperthreading (128 virtual vs. 64
physical CPUs) \todo{the fixed width on \ttt{sort}}.
% I say "we attribute" because it's a way to say something without being certain
% FIXME: We need to take linear benchmarks on deathstar and livestar to see
% where it starts dropping
% not explain scope the results appropriately
% rinard

\heading{Take-aways}

@@

\heading{Take-aways}
\sys leads to significant performance improvements in completely unmodified \unix pipelines found out in the wild.
Small tweaks can yield further improvements, showing that \sys-awareness and scripting expertise can improve results.

@@

\heading{Take-aways}
Multi-line Java Program parallel program decomposed in two phases---a highly parallel map phase and a sequential reduce phase---corresponds to a much smaller shell script with

@@

\heading{Take-aways}

@@

\heading{Take-aways}
\sys does not improve performance when running the risk of breaking correctness. % This should go in the intro
% Compared to \sys, \ttt{parallel} can lead to a combination of smaller performance improvements, incorrect execution with respect to the sequential program, and higher rewriting effort.
In highly-parallel benchmarks, \sys can lead to performance that is comparable to highly specialized streaming frameworks---at a fraction of the cost in terms of manual development.
